Prepare Data

### 2025-09-12 src/data-processing/prepare-data.Rmd
update Compendium, final submission

```{r "get & clean data", results="hide", eval=FALSE}
#Load Dutch Data
d_nl <- read_sav(here("data/raw-private/NLOZ2206_Mariken_Bias-experiment.sav"))

#Load US Data
d_us <- fetch_survey(surveyID = "SV_86XBcsFUJka9eke", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
#Clean data
source(here("src/data-processing/clean_data.R"))
```

>>>>

```{r "get & clean data", results="hide"}
#Load Dutch Data
d_nl <- read_sav(here("data/raw-private/NLOZ2206_Mariken_Bias-experiment.sav"))

#Load US Data
d_us <- readRDS(here("data/raw-private/d_us.rds"))
#d_us <- fetch_survey(surveyID = "SV_86XBcsFUJka9eke", 
#                    verbose = TRUE, force_request = T,
#                    label = FALSE, convert = FALSE)
#Clean data
source(here("src/data-processing/clean_data.R"))
```
